Bird beak's elaboration and innovation

### 2022-11-09 Analysis/05-Figure_with_phylogeny.Rmd
Update 05-Figure_with_phylogeny.Rmd

## Plot the median elaboration/innovation on the phylogeny

@@

clades <- read.csv("../Data/Processed/BirdClades.csv")
passerines <- clades$TipLabel[which(clades$level2_order=="Passeriformes")]

@@

## Save as png and pdf
ggsave("../Manuscript/Figures/InnovElabTree_passerine_supplement.png", innovelab_pass_plot, width=12, height=12)
ggsave("../Manuscript/Figures/InnovElabTree_passerine_supplement.pdf", innovelab_pass_plot, width=12, height=12)

```

>>>>

This script reproduces the figure 1 in the main manuscript (the phylogeny) and takes around 15 minutes to compile.
Note that the published figure is slightly modified in Inkscape (boxplot added manually and changed the label position for passeriformes).

# Plot the median elaboration/innovation on the phylogeny

@@

clades <- read.csv("../Data/Raw/BirdClades.csv")
passerines <- clades$TipLabel[which(clades$level2_order=="Passeriformes")]

@@

## Save as png and pdf
ggsave("../Manuscript/Figures/InnovElabTree_passerine_supplement.png", innovelab_pass_plot, width=12, height=12)
ggsave("../Manuscript/Figures/InnovElabTree_passerine_supplement.pdf", innovelab_pass_plot, width=12, height=12)
```

## Adding a panel showing the differences in elaboration and innovation across the tree

```{r}
source("../Functions/ploting.utilities.R")
colour.palette <- gg.color.hue
## Plotting the novelty for the phylo plot:
load("../Data/Processed/ploting_data.rda")
load("../Data/Processed/ploting_data_superorder.rda")
load("../Data/Processed/ploting_data_order.rda")

## Get the values
elaborations_tree  <- ploting_data$median_elaborations
innovations_tree   <- ploting_data$median_innovations
elaborations_super <- ploting_data_superorder$median_elaborations
innovations_super  <- ploting_data_superorder$median_innovations
elaborations_order <- ploting_data_order$median_elaborations
innovations_order  <- ploting_data_order$median_innovations

pdf("../Manuscript/Figures/median_novelty_distributions.pdf", height = 4, width = 8)
par(mfrow = c(1,2), bty = "n")
## Same but boxplot version
boxplot(cbind("Whole tree level"  = c(elaborations_tree, innovations_tree),
              "Super-order level" = c(elaborations_super, innovations_super),
              "Order level"       = c(elaborations_order, innovations_order)),
        xlab = "", ylab = "Elaboration/Innovation", col = colour.palette(5)[1:3])
boxplot(cbind("Elaboration" = c(elaborations_tree, elaborations_super, elaborations_order),
              "Innovation"  = c(innovations_tree, innovations_super, innovations_order)),
        xlab = "", ylab = "Elaboration/Innovation", col = colour.palette(5)[4:5])
dev.off()
```
